\documentclass[11pt,letterpaper]{article}
\usepackage[margin=0.7in,includehead,headheight=40pt]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{hyperref}
\hypersetup{colorlinks=true,urlcolor=blue}

% Contact info lives in the page header (a common ATS pitfall).
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyhead[L]{{\LARGE\textbf{Sam Okafor}}}
\fancyhead[R]{\small sam.okafor@email.com $\cdot$ (415) 555-0199 \\ \href{https://linkedin.com/in/samokafor}{linkedin.com/in/samokafor} $\cdot$ Seattle, WA}

\titleformat{\section}{\large\bfseries\scshape}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{6pt}
\setlist[itemize]{leftmargin=1.4em,itemsep=1pt,topsep=2pt}
\newcommand{\entry}[4]{\textbf{#1} \hfill #2\\ \textit{#3} \hfill \textit{#4}\par}

\begin{document}

\section{What I Do}
Full-stack developer who loves turning messy problems into clean products.
Five years building web apps end to end.

\section{Where I've Worked}
\entry{Northwind Commerce}{Seattle, WA}{Senior Developer}{2020 -- Present}
\begin{itemize}
  \item Lead developer on the customer-facing storefront, built with React and TypeScript.
  \item Designed and built Node.js backend services and GraphQL APIs used across the product.
  \item Mentored two junior engineers and ran the team's weekly design reviews.
  \item Set up CI/CD with GitHub Actions and moved deployments to AWS.
\end{itemize}

\entry{Pixel \& Co}{Portland, OR}{Web Developer}{2019 -- 2020}
\begin{itemize}
  \item Built responsive marketing sites and internal tools in JavaScript and Vue.
  \item Improved page load performance and accessibility across the client portfolio.
\end{itemize}

\section{Stack}
JavaScript, TypeScript, React, Node.js, GraphQL, Vue, HTML/CSS, AWS, GitHub Actions, PostgreSQL

\section{School}
\entry{Oregon State University}{Corvallis, OR}{B.S. Computer Science}{2015 -- 2019}

\end{document}
