\documentclass[11pt,letterpaper]{article}
\usepackage[margin=0.7in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\hypersetup{colorlinks=true,urlcolor=blue}
\pagestyle{empty}

\titleformat{\section}{\large\bfseries\scshape}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{6pt}
\setlist[itemize]{leftmargin=1.4em,itemsep=1pt,topsep=2pt}
\newcommand{\entry}[4]{\textbf{#1} \hfill #2\\ \textit{#3} \hfill \textit{#4}\par}

\begin{document}

\begin{center}
  {\LARGE \textbf{Jordan Reyes}}\\[2pt]
  Austin, TX \, $\cdot$ \, jordan.reyes@email.com \, $\cdot$ \, (512) 555-0148 \,
  $\cdot$ \, \href{https://github.com/jreyes}{github.com/jreyes}
\end{center}

\section{Summary}
Software engineer with 3 years of experience building and shipping web
applications. Comfortable across the stack with a focus on backend services
and data-heavy features.

\section{Experience}
\entry{BrightLedger (FinTech startup)}{Austin, TX}{Software Engineer}{2022 -- Present}
\begin{itemize}
  \item Built and maintained backend APIs in Python (Flask) serving the company's invoicing product.
  \item Worked with PostgreSQL to model financial data and wrote queries powering reporting dashboards.
  \item Containerized services with Docker and deployed them to AWS (EC2, RDS, S3).
  \item Added automated tests and helped set up the team's build pipeline, cutting release time.
  \item Collaborated with two other engineers on feature design and code reviews.
\end{itemize}

\entry{Cobalt Apps (Agency)}{Remote}{Junior Developer}{2021 -- 2022}
\begin{itemize}
  \item Developed client websites and small web apps using JavaScript and React.
  \item Integrated third-party REST APIs (payments, email, analytics).
  \item Fixed bugs and shipped features against tight client deadlines.
\end{itemize}

\section{Projects}
\begin{itemize}
  \item \textbf{tinyqueue} --- a small job-queue library in Python backed by Redis; ~300 GitHub stars.
  \item \textbf{budgetbot} --- a personal-finance Slack bot (Python, SQLite).
\end{itemize}

\section{Skills}
\textbf{Languages:} Python, JavaScript, SQL \\
\textbf{Frameworks/Tools:} Flask, React, Docker, Git, PostgreSQL, Redis \\
\textbf{Cloud:} AWS (EC2, RDS, S3)

\section{Education}
\entry{University of Texas at Austin}{Austin, TX}{B.S. in Computer Science}{2017 -- 2021}

\end{document}
